Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-02-08 WSSSPE4_report/WSSSPE4_report.tex
note about lightning talk list type and order
minor formatting fix

    \textbf{Track 2 -- Practices \& experiences in sustainable scientific software}
    has the goal of improving the quality of today's research software and the
    experiences of its developers by sharing practices and experiences.
    This track is focused on the current state of scientific software and what
    we can do to improve it in the short term, starting with where we are today.
\end{quote}

@@

Intro and description.
A \textsuperscript{\textasteriskcentered} indicates which author presented the
lightning talk, for those with multiple authors.
\katznote{not sure enum list is right here}
\kylenote{I'm fine with itemize, but they were in a particular order, right?}
%
\begin{enumerate}
    \item \textbf{Shoaib Sufi: \emph{The Software Sustainability Institute Fellowship
    programme; supporting the social side of research software}}~\cite{Sufi:2016ws}.
    Description
    %Didn’t want to “preach” to the community, wanted to be integrated with the
    % community, hence the fellows programme. Five attending WSSSPE this year.

>>>>

    \noindent \textbf{Track 2 -- Practices \& experiences in sustainable scientific software}
    has the goal of improving the quality of today's research software and the
    experiences of its developers by sharing practices and experiences.
    This track is focused on the current state of scientific software and what
    we can do to improve it in the short term, starting with where we are today.
\end{quote}

@@

Intro and description.
A \textsuperscript{\textasteriskcentered} indicates which author presented the
lightning talk, for those with multiple authors.
\katznote{not sure enum list is right here}
\kylenote{I'm fine with itemize, but they were in a particular order, right?}
\katznote{yes, let's go with itemize, but keep them in the same order}
%
\begin{enumerate}
    \item \textbf{Shoaib Sufi: \emph{The Software Sustainability Institute Fellowship
    programme; supporting the social side of research software}}~\cite{Sufi:2016ws}.
    Description
    %Didn’t want to “preach” to the community, wanted to be integrated with the
    % community, hence the fellows programme. Five attending WSSSPE this year.
